Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-10 paper/ms.tex
update ms
update ms (add table)

Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by our
search, along with important physical and observational properties.
\ngoods\ objects demonstrated what we viewed as unambiguous
characteristics of the CQV phenomenon in at least one TESS sector; we
refer to these as the ``gold sample''.  We found the remaining
\nmaybes\ CQV candidates to be ambiguous; their variability might be
caused by say, multiple starspot groups.  Additional data from TESS or
other instruments could help resolve their classification.  In the
following discussion, we will primarily restrict our discussion to the
gold sample.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f4.pdf}
		\vspace{-0.35cm}
		\caption{
      {\bf LP 12-502 (TIC~402980664) light curve}, where each time
      chunk represents one TESS orbit.  Data were acquired in Sectors
      18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The red
      vertical lines highlight apparently instantaneous state changes
      in the shape of the dip pattern.  The light curve is binned to
      15-minute intervals so that there are 96 points per day, and each
      point is connected by a line.  
      Data gaps longer than one missing 15-minute are not
      interpolated; if data are missing, nothing is plotted.
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

@@

>>>>

Table~\ref{tab:thetable} lists the \ncpvsfound\ objects identified by
our search.  \ngoods\ objects demonstrated what we viewed as
unambiguous characteristics of the CQV phenomenon in at least one TESS
sector; we refer to these as the ``gold sample''.  We found the
remaining \nmaybes\ CQV candidates to be ambiguous; their variability
might be caused by say, multiple starspot groups.  Additional data
from TESS or other instruments could help resolve their
classification.  The boolean \texttt{quality} column in the table divides
the two classes.  In the following discussion, we will restrict our
discussion to the gold sample.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f4.pdf}
		\vspace{-0.35cm}
		\caption{
      {\bf LP 12-502 (TIC~402980664) light curve}, where each time
      chunk represents one TESS orbit.  Data were acquired in Sectors
      18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The red
      vertical lines highlight apparently instantaneous state changes
      in the shape of the dip pattern.  The light curve is binned to
      15-minute intervals so that there are 96 points per day, and each
      point is connected by a line.  
      Data gaps longer than 15-minutes are not
      interpolated; if data are missing, nothing is plotted.
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Complex quasiperiodic variables identified in the TESS 2-minute data. \label{tab:thetable}}
%\toprule
%TIC & $T$ & $d$ & BP-RP & RUWE & $P$ & assoc & age & teff & rstar & mstar & rcr & qual & Nsectors \\
%\midrule
%\endhead
\startdata
TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & Quality & $N_{\rm sector}$ \\
-- & mag & pc & mag & -- & hr & -- & Myr & K & $R_\odot$ & $M_\odot$ & $R_\star$ & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality} flag true), and \nmaybes\ candidate CQVs (\texttt{Quality} flag false).  The machine-readable version, available online, includes additional columns for the Gaia DR2 source identifiers and parameter uncertainties.  The age uncertainties are typically $\approx \pm 10\%$,
	but can be asymmetric.  The median temperature, radius, and mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\% respectively.
	$N_{\rm sector}$ denotes the number of TESS sectors for which data are expected to be acquired between July~2018 and Oct~2024.   Association names and provenance follow conventions adopted by \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
	CAR: Carina \citep{2015MNRAS.454..593B}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
}
\end{deluxetable}
\clearpage
